Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-02-04 paper/main.tex
numerical considerations

\section{The cosmic web algorithms}
\label{sec:algorithms}
We use two algorithms to define the cosmic web on cosmological N-body
simulations. Both are based on the same algorithmic principle, which
is determining locally a symmetric tensor which can be diagonalized to yield
three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
  e}_3$. This allows for a local classification into one of the
following four categories: void, sheet, filament and peak depending
whether the number of eigenvalues larger than a given threshold
$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.

We use two different symmetric tensors. The first is the shear tensor,
defined as the hessian of the gravitational potential, normalized in
such a way as to be dimensionless:

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
%
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
is the matter overdensity, $\bar{\rho}$ is the averagematter density,
$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
matter density parameter. A detailed presentation of this algorithm
can be found in \citep{Tweb}.

@@

In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$. In the V-Web computations we compute
the velocity field as follows. First we compute the momentum density field
over a grid and the normalize it by the matter density field. We follow the
same procedure for the gaussian smoothed fields. It means that a
smoothed velocity fields is the ratio of the smoothed momentum density
and matter density fields.

>>>>

\section{Web Finding Algorithms}
\label{sec:algorithms}

We use two algorithms to define the cosmic web in cosmological N-body
simulations. Both are based on the same algorithmic principle, which
determines locally a symmetric tensor which can be diagonalized to yield
three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
  e}_3$. This allows for a local classification into one of the
following four web types: void, sheet, filament and peak depending
on the number of eigenvalues larger than a given threshold
$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.

We use two different symmetric tensors. The first is the shear tensor,
defined as the Hessian of the gravitational potential, normalized in
such a way as to be dimensionless:

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
%
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
is the matter overdensity, $\bar{\rho}$ is the average matter density,
$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
matter density parameter. A detailed presentation of this algorithm
can be found in \citep{Tweb}.

@@

In this paper we compute the cosmic web on cubic grids of two different
resolutions $256^3$ and $512^3$. For the T-Web we interpolate first
the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
smooth using a Gaussian kernel with a spatial variance equal to the
size of one grid cell. This smoothed matter density field is
transformed into Fourier space to solve the Poisson equation and find
the gravitational potential $\phi$. The Hessian is computed a finite
differences method. Finally, the eigenvalues and eigenvectors are
computed on each grid point.

For the V-Web we interpolate first the momentum density field over a
grid using the CIC scheme and then apply a gaussian smoothing with a
spatial variance of one grid cell. We use the matter density field,
which is also CIC interpolated and gaussian smoothed, to normalize the
momentum field. This ratio between the momentum and matter density
field is what we consider as the velocity field to compute the shear
tensor on each grid point. In this case we also compute the
eigenvalues and eigenvectors on each grid point.
